\subsection{August 6th, 2019}
{\Fontauri
  Regretfully, it appears I fell asleep during my surveilance, as I was abruptly
  awoken by the shouts of my party chasing after someone. I stumbled awake and
  dashed in their direction to find them cornering this young man with a cultist
  mask. Introducing himself as Lynn, a combination of Varkos' bad cop and Xori's
  good cop made him open up to us. We found out that:
  \begin{itemize}
    \item The girl is still alive, but is to be sacrificed in a ritual at
      midnight!
    \item The enterence to the cultist lair is in the graveyard (how dramatic),
      but there exists a secret enterence near the graveyard on the side of the
      sheer cliff face. There is a hidden path to it.
    \item One of them seems to have some kind of spellcasting ability, but the
      others are mostly martial combatants.
  \end{itemize}
  We ended up sending Lynn to the Zealous Dragon Inn, since his backstory seemed
  to move most of the group into sympathy. Me though, I would rather him take
  responsibility for his actions, regardless of the circumstances.

  We rushed to the graveyard and managed to directly interrupt the ritual. The
  fight was not as difficult as it could be, as Xori had an extremely well
  placed sleep that incapacitated most of the foes. The head priestess, on
  deaths door, wailing something about Shea and took her own life. This was
  unsettling, but the Oddwise seemed to be sure that nothing actually came out
  of it, and I tend to agree. The gem she dropped was the gem we were searching
  for. I picked it up and experiance an extremely exhilirating feeling of power,
  and eventually delusions of gradeur, but the feeling subsided before it
  overtook me. Xori and the Oddwise inspected the gem with me, but aside from
  the Oddwise noting that it appeared to posses every school of magic, we were
  unable to make heads or tails of the object.

  Varkos managed to get the girl untied, and she seemed to be fine, if a bit
  enamored with my bugbear friend. Good for him, I say; he could use a bit of
  a push in that direction if you get my meaning. As we were heading out, we
  encountered the beggar boy, Sadie, once more. He told us that he had managed
  to tail the cultist that had managed to dissapear (smart lad), and saw that he
  had entered the Wharf district guard house. This bodes ill, and likely
  explains why they were entirely unhelpful in the search for this poor girl.
  They must face the consequences of their actions.
}
