\subsection{July 22nd, 2019}

{\Fontauri
Today, we met Falken Towerfall, a young noble, and her guard Marisha. Varkos and
I were drinking in the tavern when I noticed a group of individuals gearing up
to attack them. Varkos and I followed two of them to the bathroom where we
defeated the thugs, with some very violent help from Marisha. One of them
mentioned a \textit{"Lord of Chaos"}, perhaps relevant. When we came out to the
main room, we learned that Falken had his gem stolen by some thugs, and some
spellcaster capable of atleast misty step (and I suspect invisibility too!) had
escaped with it. He was part a larger group of thugs who had attacked when we
stepped away, some group of travelers in the tavern had stopped them, an
eccentric group of newcomers. They seem to be competent enough, however, and
Falken hired all of his to try and track down the gem.

The noble doesn't know about the \textit{"Lord of Chaos"}, but he reccomends the
wharf districts for the criminal underbelly, specifically a captain Xendros. He
often will trade for information, but there's often a price. In addition, she
gave us a seal of the lord to help with perhaps convincing people of our
legitimacy, and offered 500 gp on the completion of the mission.

The Temple of Vionna might contain some information with regards to \textit{"The
lord of Chaos"}, specifically the head priestess; I seem to recall having
a rousing chat with her a long time ago. In addition, Varkos seems to think it
might be connected with Shea, the Evil God of Destruction and Chaos. 

We've set off to find Xendros!
}
